---
title: "Alpavantage Xtra"
output: 
  html_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

There is an Alpha Vantage SDK shipped along with Tidyquant which provided access to interday prices.
This package aims to provide R users with convenient functions to access other API features.
Starting with financial documents and IPO Calendar.

You will need a API key from Alpha Vantage which can be obtained by signing up to [](https://www.alphavantage.co/).

There is basic file based caching available which is disabled by default.  Make sure you use the cachine feature if you want to download a information for more than a handful of companies beacuase you will quickly meet API rate limits otherwise.

### Use Cases

- Intrinsic Valuation.
- Portfolio Weighting.
- Stock Selection.

R version 4.1 or higher is required.

## Basic Usage

## Set API Token

Set this environment variable in your ~/.Renviron file.  
Or set it for session with the Sys.setenv command.

```{r setup_packages}
library(alphavantagerxtra)
library(tidyverse)
# Sys.setenv("ALPHA_VANTAGE_TOKEN" = "ABCD12345")
```

## IPO Calendar
```{r ipo_calendar}
ipo_calendar <- av_get_ipo_calendar() |> t()
knitr::kable(ipo_calendar)
```

## Company Overview
```{r company_overview}
# Pause to prevent API rate limits.
Sys.sleep(10)
amazon_overview <- av_get_overview("AMZN")
names(amazon_overview)
amazon_overview |> human_readable_tibble() |> t() |> knitr::kable()
```

## Company Balance Sheet
```{r company_balance_sheet}
facebook_balance_sheet <- av_get_balance_sheet("FB")
names(facebook_balance_sheet)
facebook_balance_sheet |> 
  human_readable_tibble() |> 
  select (fiscal_date_ending:cash_and_cash_equivalents_at_carrying_value) |>
  knitr::kable()
```

## Company Cash Flow
```{r cash_flow}
# Pause to prevent API rate limits.
Sys.sleep(10)

jpmorgan_cash_flow <- av_get_cash_flow("JPM")
names(jpmorgan_cash_flow)
jpmorgan_cash_flow |> 
  human_readable_tibble() |> 
  select(fiscal_date_ending:operating_cashflow, net_income) |>
  knitr::kable()
```


## Company earnings
```{r earnings}
# Pause to prevent API rate limits.
Sys.sleep(10)

twtr_earnings <- av_get_earnings("TWTR")
names(twtr_earnings)
twtr_earnings |> 
  human_readable_tibble() |> 
  knitr::kable()
```

## Income Statement

Quarterly and Annuals earnings are returned in the same tibble.  Filter on the periodicity column to just get one type.

```{r income_statement}
# Pause to prevent API rate limits.
Sys.sleep(10)

morgan_stanley_income_statement <- av_get_income_statement("MS")
names(morgan_stanley_income_statement)
morgan_stanley_income_statement |> 
  filter(periodicity == "annual") |>
  human_readable_tibble() |> 
  select(fiscal_date_ending:total_revenue, operating_income, ebitda, net_income) |>
  knitr::kable(caption = "Annual Earnings")

morgan_stanley_income_statement |> 
  filter(periodicity == "quarterly") |>
  human_readable_tibble() |> 
  select(fiscal_date_ending:total_revenue, operating_income, ebitda, net_income) |>
  knitr::kable(caption = "Quarterly Earnings")


```

# More help

Use ?alphavantagerxtra inside your R session.

## Contact the Author
- [email Mark Hamlin @ badattribute@gmail.com](mailto:badattribute@gmail.com)
- [twitter](https://twitter.com/markchamlin)
- [https://blog.badattribute.com](https://blog.badattribute.com/)
